### 2018-02-28 Sections/cryptowars.tex
Stubs: hashing, dig sig.

@@

One of the most exciting new cryptographic applications that has emerged in recent years is the Blockchain, a secure distributed ledger\index{Distributed ledger} for recording the execution of contracts and transactions. This has enabled cryptocurrencies\index{Cryptocurrencies}, most notably Bitcoin, to emerge as a secure digital alternative to conventional fiat currencies. More recent developments, such as the Ethereum project\index{Ethereum}, develop the distributed ledger further to allow executable code to be committed to the Blockchain, opening the prospects for self-enforcement and execution of completely arbitrary contracts, a potential game-changer for the operation of financial markets.

@@

The mining process is based upon the computational hardness of implementing SHA256 hashing\index{Hashing}\index{SHA256}. A legitimate Bitcoin is defined by a string with a hash satisfying a thoughtfully chosen constraint, which associates computational complexity with the mining process, and hence computational integrity of the money supply.

@@

To address this security threat, quantum-resistant hashing and public-key cryptographic protocols will need to be developed. In the former case this can easily be achieved by increasing hash lengths so as to offset the quadratic enhancement offered by Grover's algorithm. In the latter case this will require post-quantum public-key cryptosystems (to be discussed in the next section).

>>>>

%
% Digital Signatures
%

\subsubsection{Digital signatures} \index{Digital signatures}

%
% Hashing
%

\subsubsection{Hashing} \index{Hashing}

\comment{To do. Collisions.}

@@

One of the most exciting new cryptographic applications that has emerged in recent years is the Blockchain, a secure distributed ledger\index{Distributed ledger} for recording the execution of contracts and transactions. This has enabled cryptocurrencies\index{Cryptocurrencies}, most notably Bitcoin, to emerge as a secure digital alternative to conventional fiat currencies. More recent developments, such as the Ethereum project\index{Ethereum}, develop the distributed ledger further to allow executable code to be committed to the Blockchain, opening the prospects for self-enforcement and -execution of completely arbitrary contracts, a potential game-changer for the operation of financial markets.

@@

The mining process is based upon the computational hardness of inverting SHA256 hashing\index{Hashing}\index{SHA256}. A legitimate Bitcoin is defined by a string with a hash satisfying a thoughtfully chosen constraint, which associates computational complexity with the mining process, and hence computational integrity of the money supply.

@@

To address this security threat, quantum-resistant hashing and public-key cryptographic protocols will need to be developed. In the former case this can easily be achieved by increasing hash lengths so as to offset the quadratic enhancement offered by Grover's algorithm\index{Grover's algorithm}. In the latter case this will require post-quantum public-key cryptosystems (to be discussed in the next section).
